|

### 2019-07-30 article/article.tex
add files

One of the key determinants of efficient public service provision is a
robust accountability system
\citep{besley2003incentives,cameron2004public,o1998horizontal}. In its
standard definition, accountability is the process of holding
authorities into account for their actions
\citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}.
Recent studies show that accountability ensures that politicians act on
behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing},
reduces the opportunities for rent-seeking and corruption
\citep{deininger2005does,wenar2006accountability} and increases the
efficiency of the public sector \citep{adsera2003you,bjorkman2009power}.
Moreover, greater accountability is associated with higher levels of
economic growth, not only because it limits state discretion in the
economy, but also because it promotes social cohesion and long-term
investments in human capital
\citep{benhabib2010economic, cox2018executive, suebvises2018social,ponzetto2018social}.

However, accountability systems can take many forms. One promising model
for democratic oversight is \emph{bottom-up accountability}, in which
citizens receive information about the shortcomings of a given project
to help them monitor and pressure underperforming public officials
\citep{kosack2014does, molina2016community,raffler2018weakness}.
Proponents suggest bottom-up is an effective method of accountability
because 1) constituents have first-hand information about the outcomes
of local policies; 2) citizens have incentives to avoid corruption that
directly affects them; 3) policy-makers are particularly sensitive to
social punishment from their own communities
\citep[570]{serra2011combining}. In a nutshell, bottom-up accountability
offers a potential solution to the principal-agent dilemma in public
service by aligning the interests of politicians and bureaucrats with
those of the constituency they serve \citep[2]{raffler2018weakness}.

@@

Where \(i\) indexes the case. \(Y_i\) in one the outcomes we described
in the previous subsection. The coefficient for \(\beta\) is the
quantity of interest (Average Treatment Effect). \(T_i\) is a binary
treatment indicator in which zero denotes that \(i\) is in the control
group, while 1 indicates that \(i\) received the treatment. \(\gamma\)
is a vector of fixed effects and \(X_i\) is a matrix of 27 Brazilian
states' fixed effects. \(\theta\) is a vector of additional controls and
\(Z_i\) is an array of control variables for the case \(i\). Lastly,
\(\epsilon_i\) is the error term.

>>>>

One of the key determinants of efficient public service provision is a
robust accountability system
\citep{besley2003incentives,cameron2004public,o1998horizontal}. In its
standard definition, accountability is the process of holding
authorities into account for their actions
\citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}.
Past studies show that accountability ensures that politicians act on
behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing},
reduces the opportunities for rent-seeking and corruption
\citep{deininger2005does,wenar2006accountability} and increases the
efficiency of the public sector \citep{adsera2003you,bjorkman2009power}.
Moreover, greater accountability is associated with higher levels of
economic growth, not only because it limits state discretion in the
economy, but also because it promotes social cohesion and long-term
investments in human capital
\citep{benhabib2010economic, cox2018executive, suebvises2018social,ponzetto2018social}.

However, accountability systems can take many forms. One promising model
for democratic oversight is \emph{bottom-up accountability}, in which
citizens receive information about the shortcomings of a given project
to help them monitor and pressure underperforming public officials
\citep{kosack2014does, molina2016community,raffler2018weakness}.
Proponents suggest bottom-up accountability is effective because 1)
constituents have first-hand information about the outcomes of local
policies; 2) citizens have incentives to avoid corruption that directly
affects them; 3) policy-makers are particularly sensitive to social
punishment from their own communities \citep[570]{serra2011combining}.
In a nutshell, bottom-up accountability offers a potential solution to
the principal-agent dilemma in public service by aligning the interests
of politicians and bureaucrats with those of the constituency they serve
\citep[2]{raffler2018weakness}.

@@

Where \(i\) indexes the case. \(Y_i\) in one the outcomes we described
in the previous subsection. The \(\beta\) coefficient is the quantity of
interest (Average Treatment Effect). \(T_i\) is a binary treatment
indicator in which zero denotes that \(i\) is in the control group,
while 1 indicates that \(i\) received the treatment. \(\gamma\) is a
vector of fixed effects and \(X_i\) is a matrix of 27 Brazilian states'
fixed effects. \(\theta\) is a vector of additional controls and \(Z_i\)
is an array of control variables for the case \(i\). Lastly,
\(\epsilon_i\) is the error term.
